Exploring the Impact of Queer Media Characters on LGBTQ+ Psychological Well-Being: The Role of Queer Media Consumption, Perceived Authenticity, and Intersectionality

### 2025-02-13 Queer Characters and LGBTQ+ Well-being.qmd
Dingning Yang - Project submission #1 for grading - @nrdowling @Regenchen

## Conclusion
This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts. The findings indicate that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years. The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals. While queer men may be more sensitive to authenticity due to existing stereotypes, queer women and other identities tend to benefit more from intersectional representations. Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in the media. The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diverse queer representations. It is also necessary to present bisexual characters in a non-stereotypical way to reduce biphobia and increase bisexual individuals' psychological well-being. The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups, and the lack of comparison among different media’s impacts. Future research may consider a larger sample with more balanced representation of different subgroups to further explore the psychological impacts of queer media characters on LGBTQ+ individuals. Scholars may also be interested in the intersectional analysis of different media’s impacts.

>>>>

## Conclusion
This study investigates the psychological impacts of queer media characters on LGBTQ+ individuals across different subgroups and identifies predictors of these impacts. The findings indicated that while queer media characters' psychological impacts did not significantly differ among different generations and transgender status, they were more positive for individuals living in developing countries, women and nonbinary individuals, and racial minorities, indicating a progress in queer media representations of more marginalized groups in recent years. The study also reveals that the authenticity and intersectionality of queer media characters are crucial factors in determining their psychological impacts on LGBTQ+ individuals. While queer men may be more sensitive to authenticity due to existing stereotypes, queer women and other identities tend to benefit more from intersectional representations. Additionally, bisexual individuals may experience lower psychological impacts due to the lack of authentic bisexual representations in the media. The current study enriches the understanding of different LGBTQ+ individuals' needs for queer media characters by comparative analysis, revealing the necessity for the media industry to provide LGBTQ+ audience with more authentic and diverse queer representations. It is also necessary to present bisexual characters in a non-stereotypical way to reduce biphobia and increase bisexual individuals' psychological well-being. The limitations of this study lie in the relatively small sample size, disproportionate representation of different subgroups, and the lack of comparison among different media’s impacts. Future research may consider a larger sample with more balanced representation of different subgroups to further explore the psychological impacts of queer media characters on LGBTQ+ individuals. Scholars may also be interested in the intersectional analysis of different media’s impacts.
